A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-04-05 demystify.tex
updates

While the information presented here can be useful for all students interested in CS PhD in the US, this guideline is primarily intended for \textbf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences).  
My goal is to level the playing field by providing information that is not readily available to such students.

@@

There are various guides on writing SOP , and \href{https://cs-sop.org/}{many example statements} are available. In short, focus on your research motivation and convince us that you can achieve it through your experience, e.g., published papers. You should also back up your claims with concrete evidences. For example, if you say you have experience with teaching, then show what you did, e.g., undergrad TA or mentoring someone.  If you say you work on project X, then show some results (paper submitted (or even rejected), achieved X\% performance improvement over ..).

>>>>

While the information presented here can be useful for all students interested in applying to a CS PhD program in the US, this guideline is primarily intended for \textbf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences). 
Students from top schools with strong research cultural and experiences might already know most of the information presented here.
My goal is to level the playing field by providing information that is not readily available to less privileged students.  I also hope to encourage more students from these countries to apply to CS PhD programs in the US.

@@

There are various guides on writing SOP , and \href{https://cs-sop.org/}{many example statements} are available. In short, focus on your research motivation and convince us that you can achieve it through your experience, e.g., published papers. You should also back up your claims with concrete evidences. For example, if you say you have experience with teaching, then show what you did, e.g., undergrad TA or mentoring someone.  If you say you work on project X, then show some results (paper submitted (or even rejected), achieved X\% performance improvement over ..). Also, do not use more than 2 pages (you can have references in the third page).

### 2024-04-05 faculty.tex
updates

\chapter{Research}
\chapter{Obtaining Funding}
\section{NSF and other Government Funding}

@@

>>>>

\chapter{Research}
\chapter{Obtaining Funding}
Getting funding is arguably the most important part of getting tenure.  Most new professors struggle with grant writing, which is very different than writing research papers. However, without funding, you can't pay your students, travel to conferences, or even pay your own salary. In short, the lack of funding cause lost of stress and anxiety, and threaten your tenure.  In this chapter, we will discuss the various ways to obtain funding.

\section{Most people suck at grant writing (at first)} Most new assistant professors have no experience in grant writing, and struggle with it in the beginning.  Then eventually they will get used to it and learn to like it (or at least tolerate it).  The key is to keep trying, and to not give up. The best researchers at the best universities get rejected all the time.  It's part of the process.  So don't get discouraged.  Keep trying, and you will get better over time.

\paragraph{It is very different than writing research papers} Grant writing is a very different skill than writing research papers.  In research papers, you describe what you \emph{did}. You convince people the merits of your work by showing the technical details, e.g., the algorithm,math, and proofs, and presenting experiments and results supporting your claim. You don't need to tell people who you are (often the authors are anonymous), and you don't need to convince people that you are the right person to do the work.  Your reviewers are typically experts in your field and know a bit about the paper topic, and they are judging your work based on the technical merits.

In grant writing, you are trying to convince people to give you money to do something you \emph{haven't done yet}.  You need to convince people at a much higher level that your idea is important (impactful) and that you are the right person (with the right collaboration, resource, and plan) to do it. Getting too much into technical details can be a turn off.  Your reviewers might not also experts in your field, and they are judging your work based on the \emph{big picture}.

However, it's a skill that can be learned.  The best way to learn is to read other people's grants, and to write your own.  You will likely get rejected many times, but that's normal.  You will get better over time.  The key is to keep trying, and to not give up.  If you are not getting rejected, you are not aiming high enough.  The best researchers in the world get rejected all the time.  It's part of the process.  So don't get discouraged.  Keep trying, and you will get better over time.

It's a very different skill than writing research papers.  However, it's a skill that can be learned.  The best way to learn is to read other people's grants, and to write your own.  You will likely get rejected many times, but that's normal.  You will get better over time.  The key is to keep trying, and to not give up.  If you are not getting rejected, you are not aiming high enough.  The best researchers in the world get rejected all the time.  It's part of the process.  So don't get discouraged.  Keep trying, and you will get better over time.
\section{NSF and other Government Funding}

@@

\appendix
\chapter{NSF Panel Reviews}
